Ecuador plant species POWO

### 2022-10-12 code/L0/L0_Ecuador_plants_POWO.Rmd
fix na summary save as csv

# Summary
```{r}
summary(Ecuador_POWO)
na_summary(Ecuador_POWO)
```

# Write data to csv
```{r}
Ecuador_POWO_path <- file.path(output_path, "Ecuador_POWO.csv")
write.csv(Ecuador_POWO, file = Ecuador_POWO_path)
```

>>>>

# Summary
```{r}
summary(Ecuador_POWO)
na_summary(Ecuador_POWO, exclude_cols = c("accepted", "url", "images"))
```

# Write data to csv
```{r}
#convert Ecuador_POWO from tbl_df to dataframe
Ecuador_POWO <- as.data.frame(Ecuador_POWO)
# remove image column from dataframe
Ecuador_POWO <- Ecuador_POWO %>% select(-images)

Ecuador_POWO_path <- file.path(output_path, "Ecuador_POWO.csv")
write.csv(Ecuador_POWO, file = Ecuador_POWO_path)
```
